Asymmetric continuous prediction bands for assessing the validity of smooth biomechanical curve data

### 2021-09-20 paper.Rmd
Implement new data sets

### Synthetic data sets

To compare different methods for constructing continuous LoA, several sets of smooth curve data were simulated across a range of common biomechanical signals and error characteristics. The quality of the curves is similar, as the paper is primarily developed for a validation context in which the same movement process is analyzed using similar methods (two measurement devices or models). For the same reason, the curves do not necessarily correspond to real-world signals as we were more concerned with illustrating the respective methods and error characterstics.

@@

### Smooth curves (homoscedasticity, normal error, no trend)

```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "smooth", dir.data)

@@

### Smooth curves with nonlinear error trend

```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "smooth_trend", dir.data)

@@

#### Heteroscedasticity across the signal length

<!-- Smooth curves with non-gaussian (Weibull) error (no trend) -->

@@

#### Curves phase shifted in x-axis direction

@@

### Cross validation

Leave-one (curve) out method to estimate the achieved coverage

@@

### Functional limits of agreement

```{r echo = FALSE, warning = FALSE, message = FALSE}
n.boot <- 400

### Leave-one (curve) out cross validation

Displayed are boxes for five different methods:

* 1. FLoA~RCB_v2~ : One random stride per subject

* 2. FLoA~RCB_v3~ : Fetch a SINGLE random stride from all strides

* 3. FLoA~Roislien~ : Roislien approach (Get one random stride from each subject ONCE and boot-
       strap the resulting sample (of length (n=length(subjects))

* 4. FLoA~Point~ : Pointwise B & A Limits of Agreement (SD derived from linear mixed effects model)

Coverages are displayed for two different scenarios:

@@

* c: Uncertainty in LoA (95% percentile intervals)

#### Smooth, wave data (normal error, constant variance, no trend)

```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "smooth", dir.data)

@@

@@

#### Curves with nonlinear trend (constant variance)

```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "smooth_trend", dir.data)

@@

knitr::kable(covered.curves.percent, caption = "Percentages of entire covered curves")
```

cover.cross.mean.sd <- rbind(round(colMeans(cover.cross.fraction.singlecurve), 2),
             round(apply(cover.cross.fraction.singlecurve, 2, sd), 2)
)
knitr::kable(cover.cross.mean.sd, caption = "Mean (top) and SD of covered points across the curve")
```

@@

#### Curves phase shifted in x-axis direction

@@

>>>>

### Data generating process
To compare different methods for constructing continuous LoA, several sets of smooth curve data were simulated across a range of common biomechanical signals and error characteristics. The quality of the curves is similar, as the paper is primarily developed for a validation context in which the same movement process is analyzed using similar methods (two measurement devices or models). For the same reason, the curves do not necessarily correspond to real-world signals as we were more concerned with illustrating the respective methods and error characterstics.

@@

### Realistic smooth wave data (constant variance, no trend)
```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "smooth_realistic", dir.data)

@@

### Smooth curves (homoscedasticity, normal error, no trend)
```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "smooth", dir.data)

@@

<!-- ### Smooth curves with nonlinear error trend -->
<!-- ```{r echo = FALSE, warning = FALSE, message = FALSE} -->
<!-- data <- example_data(dat = "smooth_trend", dir.data) -->

<!-- data.single.mc <- subset(data, device == "MC") -->
<!-- data.single.imu <- subset(data, device == "IMU") -->

<!-- PLOT <- ggplot(data = data.single.mc, aes(x = frame, y = value, group = strideID)) + -->
<!--   geom_line() + -->
<!--   scale_color_grey(start = 0.6, end = 0.9) + -->
<!--   geom_line(data = data.single.imu, aes(x = frame, y = value, group = strideID, colour = as.factor(subjectID)), alpha = 0.3) + -->
<!--   labs(x = "Time-normalized signal [%]", y = "Signal value") + -->
<!--   theme_minimal() + -->
<!--   theme(axis.text.x = element_text(size = 20), -->
<!--         axis.title.x = element_text(size = 18), -->
<!--         axis.text.y = element_text(size = 20), -->
<!--         axis.title.y = element_text(size = 18), -->
<!--         legend.position = "none") -->

<!-- PLOT -->
<!-- ``` -->

#### Heteroscedasticity across the signal length
<!-- Smooth curves with non-gaussian (Weibull) error (no trend) -->
```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "non_gaussian", dir.data)

@@

#### Curves phase shifted in x-axis direction
```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "shift", dir.data)

@@

#### Real-world validation data
```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "imu_mc", dir.data)

### Leave-one (curve) out cross validation
Leave-one (curve) out method to estimate the achieved coverage

@@

#### Coverages
Coverages are displayed for two different scenarios:

@@

### LoA uncertainty
In order to quantify the uncertainty of the calculated LoA across different methods, LoA were calculated n.boot times and compared using uncertainty bands.

### Functional limits of agreement
```{r echo = FALSE, warning = FALSE, message = FALSE}
n.boot <- 1000

### Leave-one (curve) out cross validation
Displayed are boxes for different calculation methods (FLoA~RCB_v2~, FLoA~RCB_v3~, FLoA~Roislien~, FLoA~Point~)

#### Realistic smooth wave data (constant variance, no trend)
a. Coverage of the entire curve
```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "smooth_realistic", dir.data)

@@

b. Mean (SD) of covered curve points
```{r echo = FALSE, warning = FALSE, message = FALSE}
# Leave-one curve out approach
# ------------------------------------------------------------------------------
cover.cross.fraction.singlecurve <- singlecurve_coverage_fraction(data, n.boot)

@@

c. Uncertainty in LoA (95% percentile intervals)
```{r echo = FALSE, warning = FALSE, message = FALSE}
estimate_uncertainty_loa(data, n.boot)
```

#### Smooth, wave data (normal error, constant variance, no trend)
a. Coverage of the entire curve
```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "smooth", dir.data)

@@

b. Mean (SD) of covered curve points
```{r echo = FALSE, warning = FALSE, message = FALSE}
# Leave-one curve out approach
# ------------------------------------------------------------------------------
cover.cross.fraction.singlecurve <- singlecurve_coverage_fraction(data, n.boot)

c. Uncertainty in LoA (95% percentile intervals)
```{r echo = FALSE, warning = FALSE, message = FALSE}
estimate_uncertainty_loa(data, n.boot)
```

<!-- #### Curves with nonlinear trend (constant variance) -->

<!-- a. Coverage of the entire curve -->

<!-- ```{r echo = FALSE, warning = FALSE, message = FALSE} -->
<!-- data <- example_data(dat = "smooth_trend", dir.data) -->

<!-- # Leave-one curve out approach -->
<!-- # ------------------------------------------------------------------------------ -->
<!-- cover.cross.singlecurve <- singlecurve_coverage(data, n.boot) -->

<!-- # Calculate percent from counts -->
<!-- calculate_percent <- function(data) { -->
<!--   percentage <- (sum(data) / length(data)) -->
<!--   percentage <- round(percentage, digits = 2) -->
<!-- } -->

<!-- covered.curves.percent <- apply(cover.cross.singlecurve, 2, calculate_percent) -->
<!-- covered.curves.percent <- data.frame(t(covered.curves.percent)) -->
<!-- colnames(covered.curves.percent) <- c("RCB_2", "RCB_3", "Roislien_4", "Point_5") -->

<!-- knitr::kable(covered.curves.percent, caption = "Percentages of entire covered curves") -->
<!-- ``` -->

<!-- b. Mean (SD) of covered curve points -->

<!-- ```{r echo = FALSE, warning = FALSE, message = FALSE} -->
<!-- # Leave-one curve out approach -->
<!-- # ------------------------------------------------------------------------------ -->
<!-- cover.cross.fraction.singlecurve <- singlecurve_coverage_fraction(data, n.boot) -->

<!-- cover.cross.mean.sd <- rbind(round(colMeans(cover.cross.fraction.singlecurve), 2), -->
<!--              round(apply(cover.cross.fraction.singlecurve, 2, sd), 2) -->
<!-- ) -->
<!-- knitr::kable(cover.cross.mean.sd, caption = "Mean (top) and SD of covered points across the curve") -->
<!-- ``` -->

<!-- c. Uncertainty in LoA (95% percentile intervals) -->

<!-- ```{r echo = FALSE, warning = FALSE, message = FALSE} -->
<!-- estimate_uncertainty_loa(data, n.boot) -->
<!-- ``` -->

@@

#### Curves phase shifted in x-axis direction
a. Coverage of the entire curve

@@

#### Real-world validation data
a. Coverage of the entire curve

```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "imu_mc", dir.data)
